Quantitative Auditing of Fairness Measures with Differentially Private Synthetic Data

### 2024-11-29 paper/paper.tex
changed refs

TODO: remove all names of ryan meckenna. use references

@@

For the competition, \cite{McKenna_privatePGM,mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset. For example, he manually added the clique (sex,city,income). In addition, he would add some edges based on some sophisticated heuristics tailored to that particular dataset. Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.

>>>>

@@

For the competition, \cite{McKenna_privatePGM,mckenna2021winning} further manually added certain cliques based on his investigation of the competition dataset. For example, they manually added the clique (sex,city,income). In addition, they would add some edges based on some sophisticated heuristics tailored to that particular dataset. Meanwhile, his other apporach where the auditor does access the real dataset does not fit our framework.
